Printer ballistics through character's texture analysis

### 2013-11-19 Printer_Ballistics.tex
mais edição...

@@

@@

>>>>

\subsection{Characters}

@@

\subsection{Printers}

@@

By working in this way, page printers do not maintain a characteristic pattern that is repeated line by line across the printed sheet of paper. Due to small imperfections that may exist in the photoreceptor drum, each print area generated by this type of device can present different characteristics.
Taking into account this fact, it was necessary to obtain characters from different parts of the scanned document. Basically, each document has roughly divided into three parts: upper, middle, and bottom. The Figure \ref{fig:document_areas} shows an example of a document divided in this way. If this article is being viewed in color, the upper part of the figure is in red, the middle, in green and bottom, in blue.

\begin{figure}
\begin{center}
	\includegraphics[width=0.99\columnwidth]{document_areas}
	\caption{Division of the scanned document in areas.}
\label{fig:document_areas}   
\end{center} 
\end{figure}

Despite showing subtle differences between characters located in different areas of the printout, the print device maintains certain intrinsic characteristics unchanged in all printed characters. Such characteristics can be compared to our fingerprints, making it a way to link a printed character to a particular device.
